### 2018-11-28 VV556/HW9/submission.tex
part of hw9 sol

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW8 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\section{Exercise8.1}
	\begin{enumerate}
		\item 
			\begin{proof}
				Since
				\begin{equation}
					\sum_{i=1}^{\infty}\sum_{j=1}^{\infty}|a_{ij}|^2 = \sum_{k=1}^{\infty} \frac{1}{k} \rightarrow \infty
				\end{equation}
				Thus, $L$ is not a Hilbert-Schmidt operator.
			\end{proof}
		\item 
			\begin{proof}
				$\forall x, y \in l^2$, the inner product can be expressed as
				\begin{equation}
					\begin{aligned}
						<x, Ly> & =  <(x_1, x_2, ... , x_n, ...), (y_1, \frac{y_2}{\sqrt{2}}, ... , \frac{y_n}{\sqrt{n}}, ...)>\\
								& = \sum_{i=1}^{\infty} \frac{x_i y_i}{\sqrt{i}}\\
								& = <(x_1, \frac{x_2}{\sqrt{2}}, ... , \frac{x_n}{\sqrt{n}}, ...), (y_1, y_2, ... , y_n, ...)>\\
								& = <Lx, y>
					\end{aligned}
				\end{equation}
				Thus, $L$ is self adjoint.
			\end{proof}
		\item 
			\begin{proof}
				Denote $L_n : l^2 \rightarrow l^2$ by
				\begin{equation}
					L_n(x_n) = (x_1, \frac{x_2}{\sqrt{2}}, \frac{x_3}{\sqrt{3}}, ... , \frac{x_n}{\sqrt{n}}, 0, 0, ...)
				\end{equation}
				$L_n$ is a Hilbert-Schmidt operator as 
				\begin{equation}
					\sum_{i=1}^{\infty}\sum_{j=1}^{\infty}|a_{ij}|^2 = \sum_{k=1}^{n} \frac{1}{k} < \infty
				\end{equation}
				Thus, $L_n$ is compact. Then, $L$ is compact if $(L_n)$ converges to $L$ in norm, i.e.
				\begin{equation}
					\lim\limits_{n \rightarrow \infty} ||L_n - L|| = 0
				\end{equation}
				To show this, expand the operator norm as
				\begin{equation}
					\begin{aligned}
						||L_n - L||& = \sup\limits_{x\in l^2}\frac{||(L_n - L)x||}{||x||}\\
						& = \sup\limits_{x\in l^2}\frac{||(0, ... , 0, \frac{x_{n+1}}{\sqrt{n+1}}, \frac{x_{n+2}}{\sqrt{n+2}},...)||}{||x||}\\
						& \leq \frac{1}{\sqrt{n+1}} \frac{||(0, ... , 0, x_{n+1}, x_{n+2}, ...)||}{||x||}\\
						& \leq  \frac{1}{\sqrt{n+1}}
					\end{aligned}
				\end{equation}
				So, $\lim\limits_{n \rightarrow \infty} ||L_n - L|| \leq  \lim\limits_{n \rightarrow \infty} \frac{1}{\sqrt{n+1}} = 0$.\\
				According to the positivity of norm,  $\lim\limits_{n \rightarrow \infty} ||L_n - L||\geq 0$.\\
				Hence  $\lim\limits_{n \rightarrow \infty} ||L_n - L|| = 0$.
			\end{proof}
		\item
			Since
			\begin{equation}
				||L|| = \sup\limits_{x\in l^2} \frac{||Lx||}{||x||} \geq \frac{||Le_1||}{||e_1||} = 1
			\end{equation}
			and
			\begin{equation}
				||L|| = \sup\limits_{x\in l^2} \frac{||Lx||}{||x||} \leq \frac{||x||}{||x||} = 1
			\end{equation}
			Thus $||L|| = 1$.\\
			As the norm of operator is a bound for all its eigenvalues, then $|\lambda| \leq 1$. Thus the upper bound for the spcetrum is found.\\
			For the lower bound, Rayleigh Quotient is used. For $x\neq 0$, 
			\begin{equation}
				\lambda \geq L_T \triangleq \inf\limits_{x\in dom(L)} R(x) = \inf\limits_{x\in dom(L)} \frac{<x, Lx>}{||x||^2} = \lim\limits_{n \rightarrow \infty} \frac{<e_n, Le_n>}{||e_n||^2} = \lim\limits_{n \rightarrow \infty} \frac{1}{\sqrt{n}} = 0
			\end{equation}
			Thus the lower bound for the spcetrum is found.
		\item 
			Clearly, $\{1, \frac{1}{\sqrt{2}}, \frac{1}{\sqrt{3}}, ...\}$ is the point specturm as they are eigenvalues of $L$.

\section{Exercise8.2}
	\begin{enumerate}
		\item 
			\begin{proof}
				$\forall u \in M$, with the B.C. of $u$, the transform by operator $KL$ yields
				\begin{equation}
					\begin{aligned}
						(KL)u(x) & = \int_{0}^{1} g(x, \xi) (Lu)(\xi) d\xi\\
					 			 & = \int_{0}^{x} g(x, \xi) (Lu)(\xi) d\xi + \int_{x}^{1} g(x, \xi) (Lu)(\xi) d\xi\\
					 			 & = \int_{0}^{x} \xi(x-1) u^{\prime\prime}(\xi) d\xi + \int_{x}^{1} x(\xi - 1) u^{\prime\prime}(\xi) d\xi\\
					 			 & = \int_{0}^{x} \xi(x-1) du^{\prime}(\xi) + \int_{x}^{1} x(\xi - 1) du^{\prime}(\xi)\\
					 			 & = (\xi(x-1)u')\Big|_0^x - \int_{0}^{x} u' (x-1) d\xi + (x(\xi-1)u')\Big|_x^1 - \int_{x}^{1} u' x d\xi\\
					 			 & = x(x-1)u'(x) - (x-1) (u(x) - u(0)) - x(x-1)u'(x) - x (u(1)-u(x))\\
					 			 & = u(x)
					\end{aligned}
				\end{equation}
				Thus, $KL = I$ on $M$.
			\end{proof}
		\item 
			\begin{proof}
				For example, take $u(x) = \sqrt{x}$, then
				\begin{equation}
					||L|| \geq \frac{||Lu||}{||u||} = \frac{||x^{-\frac{3}{2}}||}{4||x^\frac{1}{2}||} \rightarrow \infty
				\end{equation}
				Thus, $L$ is unbounded.
			\end{proof}
		\item

		\item 
			\begin{proof}
				Swap $\xi$ and $x$, then
				\begin{equation}
					g(\xi, x) = 
					\left\{
						\begin{aligned}
							\xi(1-x) & \quad \xi<x\\
							x(1-\xi) & \quad \xi\geq x
						\end{aligned}
					\right.
					=
					\left\{
						\begin{aligned}
							x(1-\xi) & \quad x < \xi\\
							\xi(1-x) & \quad x \geq \xi
						\end{aligned}
					\right.
					=g(x,\xi)
				\end{equation}
				Thus, $\forall u, v\in M$,
				\begin{equation}
					\begin{aligned}
						<u, Kv> & = \int_{0}^{1} u(x) \Bigg(\int_{0}^{1} g(x, \xi) v(\xi) d\xi\Bigg) dx\\
								& = \int_{0}^{1} \int_{0}^{1} u(x) g(\xi, x) v(\xi) d\xi dx\\
								& = \int_{0}^{1} \Bigg(\int_{0}^{1} g(\xi, x) u(x) dx\Bigg) v(\xi) d\xi\\
								& = <Ku, v>
					\end{aligned}
				\end{equation}
				Hence, $K$ is self-adjoint.
			\end{proof}
		\item 
			\begin{equation}
				L_T = \inf\limits_{u\in M} \frac{<u, Ku>}{<u, u>} = \inf\limits_{u\in M} \frac{<Ku, u>}{<u, u>}
			\end{equation}
			and
			\begin{equation}
				U_T = \sup\limits_{u\in M} \frac{<u, Ku>}{<u, u>} = \sup\limits_{u\in M} \frac{<Ku, u>}{<u, u>}
			\end{equation}

>>>>

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW9 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\section{Exercise9.1}
	\begin{enumerate}
		\item
			\begin{proof}
				Since
				\begin{equation}
					\begin{aligned}
						(LKu)(x) & = -\frac{d^2}{d x^2} \int_{0}^{1} g(x, \xi) u(\xi) d\xi\\
								 & = -\frac{d^2}{d x^2} \Bigg(\int_{0}^{x} g(x, \xi) u(\xi) d\xi + \int_{x}^{1} g(x, \xi) u(\xi) d\xi \Bigg)\\
								 & = -\frac{d^2}{d x^2} \Bigg(\int_{0}^{x} \xi(1-x) u(\xi) d\xi + \int_{x}^{1} x(1-\xi) u(\xi) d\xi \Bigg)\\
								 & = -\frac{d^2}{d x^2} \Bigg((1-x)\int_{0}^{x} \xi u(\xi) d\xi + x\int_{x}^{1} (1-\xi) u(\xi) d\xi \Bigg)\\
								 & = -\frac{d}{d x} \Bigg(-\int_{0}^{x} \xi u(\xi) d\xi + \int_{x}^{1} (1-\xi) u(\xi) d\xi \Bigg)\\
								 & = xu(x) + (1-x) u(x) = u(x)
 					\end{aligned}
				\end{equation}
				Thus, $LK=I$, which means $L = K^{-1}$.
			\end{proof}
		\item 
			\begin{proof}
				($\Rightarrow$) Suppose $\frac{1}{\lambda}$ is an eigenvalue for $K$, then
				\begin{equation}
					ku = \frac{1}{\lambda}u
				\end{equation} 
				Thus
				\begin{equation}
					u = \lambda K u
				\end{equation}
				Take the operator $L$ on it
				\begin{equation}
					Lu = \lambda LKu = \lambda Iu = \lambda u
				\end{equation}
				which indicates that $\lambda$ is an eigenvalue of $L$.\\
				($\Leftarrow$) Suppose $\lambda \neq 0$ is an eigenvalue of $L$, then
				\begin{equation}
					Lu = \lambda u
				\end{equation}
				Thus
				\begin{equation}
					u = \frac{1}{\lambda} Lu
				\end{equation}
				As $K = L^{-1}$ is known, take the operator $K$ onto it yields
				\begin{equation}
					Ku = \frac{1}{\lambda}KLu = \frac{1}{\lambda} Iu = \frac{1}{\lambda} u
				\end{equation}
				which indicates that $\frac{1}{\lambda}$ is an eigenvalue of $K$.\\
				It's clear that for the given $\lambda$, $K$ and $L$ share the same eigenfunction $u(x)$.
			\end{proof}
		\item 
			\begin{proof}
				It's obvious that $L$ is bounded over $M$.\\
				Since
				\begin{equation}
					\begin{aligned}
						<u, Lv> &= -\int_{0}^{1} u(x)v''(x) dx = -\Bigg(u(x)v'(x)\Big|_0^1 - \int_{0}^{1}u'(x)v'(x)dx\Bigg)\\
								&= \int_{0}^{1}u'(x)v'(x)dx = \int_{0}^{1}u'(x)dv(x) = u'(x)v(x)\Big|_0^1 - \int_{0}^{1} v(x)u''(x)dx\\
								& = -\int_{0}^{1} u''(x)v(x)dx = <Lu, v>
					\end{aligned}
				\end{equation}
				which indicates that $L$ is self-adjoint. Thus the eigenvalues of $L$ are real numbers.\\
		 		The eigenfunction $\psi_n(x)$ of $L$ together with $\lambda_n$ satisfy 
		 		\begin{equation}
		 			\psi_n''(x) + \lambda_n \psi_n(x) = 0
		 		\end{equation}
		 		and
		 		\begin{equation}
		 			\psi_n(0) = \psi_n(1) = 0
		 		\end{equation}
		 		Solution of this ODE depends on the sign of $\lambda_n$.\\
		 		\begin{enumerate}
		 			\item 
		 				If $\lambda_n > 0$, then
		 				\begin{equation}
		 					\psi_n(x) = C_1 sin(\sqrt{\lambda_n}x) + C_2 cos(\sqrt{\lambda_n}x)
		 				\end{equation}
		 				apply the boundary condition yields
		 				\begin{equation}
		 					C_2 = 0
		 				\end{equation}
		 				and
		 				\begin{equation}
		 					C_1 sin(\sqrt{\lambda_n}) = 0
		 				\end{equation}
		 				Thus
		 				\begin{equation}
		 					\lambda_n = (n\pi)^2
		 				\end{equation}
		 				and
		 				\begin{equation}
		 					\psi_n(x) = C_2 sin(n\pi x) \quad (C_2 \neq 0)
		 				\end{equation}
		 			\item 
		 				If $\lambda_n = 0$, then
		 				\begin{equation}
		 					\psi_n(x) = C_0 + C_1 x
		 				\end{equation}
		 				Apply the B.C. yields $C_0 = C_1 = 0$, which indicates 0 is not an eigenvalue for $L$.
		 			\item 
		 				If $\lambda_n < 0$, then
		 				\begin{equation}
		 					\psi_n(x) = C_1 e^{\sqrt{-\lambda_n}x} + C_2 e^{-\sqrt{-\lambda_n}x}
		 				\end{equation}
		 				Apply the B.C. yields $C_0 = C_1 = 0$, which indicates  $\lambda_n < 0$ are not eigenvalues for $L$.
		 		\end{enumerate}
			\end{proof}
		\item

		\item
